\MakeUppercase{The Structure of $k$-Planar Graphs}

### 2019-07-08 k-planar.tex
Changed notation from k to t in MakeWidth1

\begin{thm}
\label{ShortcutProduct}
Let $G$ be a subgraph of $H\boxtimes P$, for some graph $H$ of treewidth at most $t$ and for some path $P$. 
Let $\PP$ be a $(k,d)$-shortcut system for $G$. Then $G^\PP$ is a subgraph of $J\boxtimes P$ for some graph $J$ of treewidth at most $d(k^3+k^2+4k)\binom{k+t}{t}-1$ and some path $P$. 
\end{thm}

@@

\begin{lem}[\citep{dujmovic.joret.ea:planar}] 
\label{MakeWidth1}
If a graph $G$ has an $H$-partition of layered width $\ell$ with respect to layering $\langle V_0,V_1,\dots\rangle$, for some graph $H$ of treewidth at most $k$, then $G$ has an $H'$-partition of layered width 1 with respect to the same layering, for some graph $H'$ of treewidth at most $(k+1)\ell-1$.  That is, if $G\subseteq H\boxtimes P\boxtimes K_\ell$ for some graph $H$ of treewidth at most $k$  and for some path $P$, then $G\subseteq H' \boxtimes P$ for some graph $H'$ of treewidth at most $(k+1)\ell-1$.
\end{lem}

>>>>

\begin{thm}
\label{ShortcutProduct}
Let $G$ be a subgraph of $H\boxtimes P$, for some graph $H$ of treewidth at most $t$ and for some path $P$. 
Let $\PP$ be a $(k,d)$-shortcut system for $G$. Then $G^\PP$ is a subgraph of $J\boxtimes P$ for some graph $J$ of treewidth at most $d(k^3+3k)\binom{k+t}{t}-1$ and some path $P$. 
\end{thm}

@@

\begin{lem}[\citep{dujmovic.joret.ea:planar}] 
\label{MakeWidth1}
If a graph $G$ has an $H$-partition of layered width $\ell$ with respect to layering $\langle V_0,V_1,\dots\rangle$, for some graph $H$ of treewidth at most $t$, then $G$ has an $H'$-partition of layered width 1 with respect to the same layering, for some graph $H'$ of treewidth at most $(t+1)\ell-1$.  That is, if $G\subseteq H\boxtimes P\boxtimes K_\ell$ for some graph $H$ of treewidth at most $t$  and for some path $P$, then $G\subseteq H' \boxtimes P$ for some graph $H'$ of treewidth at most $(t+1)\ell-1$.
\end{lem}
